The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-10 paper/ms.tex
seasons

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ which were unobserved for more than $8$ quarters, including those stars which were entirely unobserved. A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, the seasons for which they were on silicon (some did not even land on silicon for all seasons), and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}. Aside from the restriction on stars falling on the edge of a chip, the addition of these objects to conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$. In Figure~\ref{hrdiagram} we show these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, and situate these in context with the entire \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch. From the HR diagram, we identify 64 of these objects as evolved systems, and the remaining~38 lie on the main sequence. One of the main sequence objects, BD+43~3068 is a G0 dwarf with a $G$ magnitude of 8.267944 and a distance of $53.8 \pm 0.1$~pc, and it is therefore surprising that it was not included in the nominal \kepler survey as a Solar analogue: it is possible that it was previously misidentified as a giant. Regrettably, it is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star.

>>>>

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ which were unobserved for more than $8$ quarters, including those stars which were entirely unobserved. A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}. The \kepler satellite rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. Aside from the restriction on stars falling on the edge of a chip like tihs or otherwise, the addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$. In Figure~\ref{hrdiagram} we show these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, and situate these in context with the entire \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch. From the HR diagram, we identify 64 of these objects as evolved systems, and the remaining~38 lie on the main sequence. One of the main sequence objects, BD+43~3068 is a G0 dwarf with a $G$ magnitude of 8.267944 and a distance of $53.8 \pm 0.1$~pc, and it is therefore surprising that it was not included in the nominal \kepler survey as a Solar analogue: it is possible that it was previously misidentified as a giant. Regrettably, it is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star.
